Correlation

### 2022-03-23 graphs_newt_snakes/Correlation.Rmd
I put in the wild cards for the snakemake file. I also looked more at the correlations

cors_by_gen <- function(file, title, subt, x_label, y_label){

plot <- ggplot(file) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = subt) +
  xlab(x_label) + ylab(y_label)+
  geom_line(aes(x=as.numeric(gen), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "mean_newt_pheno_By_mean_snake_pheno"))+
  geom_line(aes(x=as.numeric(gen), y=as.numeric(num_newts_By_num_snakes), color = "num_newts_By_num_snakes"))+
  geom_line(aes(x=as.numeric(gen), y=as.numeric(sum_newt_pheno_By_num_snake), color = "sum_newt_pheno_By_num_snake"))+
  geom_line(aes(x=as.numeric(gen), y=as.numeric(sum_snake_pheno_By_num_newt), color = "sum_snake_pheno_By_num_newt"))+
  theme(plot.title = element_text(size=5)) +

@@

>>>>

cors_by_gen <- function(file, title, subt, x_label, y_label){
  print("TA = mean_newt_pheno_By_mean_snake_pheno")
  print("TB = num_newts_By_num_snakes")
  print("TC = sum_newt_pheno_By_num_snake")
  print("TD = sum_snake_pheno_By_num_newt")

  plot <- ggplot(file) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = subt) +
  xlab(x_label) + ylab(y_label)+
  geom_line(aes(x=as.numeric(gen), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "TA"))+
  geom_line(aes(x=as.numeric(gen), y=as.numeric(num_newts_By_num_snakes), color = "TB"))+
  geom_line(aes(x=as.numeric(gen), y=as.numeric(sum_newt_pheno_By_num_snake), color = "TC"))+
  geom_line(aes(x=as.numeric(gen), y=as.numeric(sum_snake_pheno_By_num_newt), color = "TD"))+
  theme(plot.title = element_text(size=5)) +

@@

title="Space: Newt VS Snake"
subt="5,000 Gen Grid 5 by 5"
y_label="Generation"
x_label="Correlation"
my_letter="A"
subt=paste0("Sim ", subt, " ", my_letter)
cors_by_gen(cor_5000_file[which(cor_5000_file$sim==my_letter), ], title, subt, x_label, y_label)
